Single-cell virus sequencing of influenza infections that trigger innate immunity

### 2018-12-27 paper/paper.tex
finished updating last section of Results to emphasize stochasticity

We tested the rate of IFN induction by each viral stock using the reporter cells.
\FIG{validation} shows that five of the eight mutant viral stocks induced IFN more frequently than a wild type viral stock.
The strongest IFN induction was by the NS1stop virus, but the PB1 internal deletion and three of the point-mutant viruses (PB1-D27N, PB1-T677A, and NS1-A122V) also induced IFN significantly more frequently than wild type.
The other three point mutants (PB1-G206S, PB1-K279R, and NS2-E47G) did not increase IFN induction---an unsurprising finding, since we also expect some mutations without an IFN-enhancing effect to be found in IFN+ cells by chance.
But overall, the results in \FIG{validation} validate that the viral defects in single IFN+ cells often cause increased IFN production.

However, IFN induction remains stochastic even for the most strongly IFN-inducing viral mutants.
\FIG{validation} shows flow cytometry data (see also \SUPPFIG{validationflow}), which is itself a single-cell measurement, albeit one that does not report the viral genotype.
All the viral mutants induce IFN in less than a fifth of cells

>>>>

We tested the rate of IFN induction by each viral stock using the reporter cells.
\FIG{validation} shows that five of the eight mutant viral stocks induced IFN more frequently than a wild-type viral stock.
The strongest IFN induction was by the NS1stop virus, but the PB1 internal deletion and three point-mutant viruses (PB1-D27N, PB1-T677A, and NS1-A122V) also induced IFN more frequently than wild type.
The other three point mutants (PB1-G206S, PB1-K279R, and NS2-E47G) did not increase IFN induction---an unsurprising finding, since we expect some mutations to be found in IFN+ cells by chance.
Overall, the results in \FIG{validation} validate that the viral defects in single IFN+ cells often increase IFN induction.

However, IFN induction remains stochastic even for the most potently IFN-inducing viral mutants.
\FIG{validation} shows flow cytometry data (see also \SUPPFIG{validationflow}), which is itself a single-cell measurement, albeit one that does not report the genotype.
These flow cytometry data reveal that no mutant virus stock induces IFN in more than a fraction of cells.
Of course, these mutant virus stocks are themselves genetically heterogeneous, as many virions will have additional defects similar to that revealed by our single-cell sequencing of the ``wild-type'' viral stock.
But IFN induction is stochastic at the single-cell level even for infections that share the same defect,such as absence of NS (e.g., compare \textit{cell 62} and \textit{cell 69} in \FIG{genotypes}).
Therefore, the experiments in this section not only validate some specific viral defects that increase IFN induction, but also show that induction is stochastic even with these defects.

\jdbcomment{Perhaps also add NS+ / NS- data here}
